\documentclass[12pt,answers]{exam}
\usepackage{amsmath}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{pifont,enumerate,color}

\newcommand{\reals}{\mathbf{R}}
\newcommand{\integers}{\mathbf{Z}}

\newenvironment{alphalist}{
  \begin{enumerate}[(a)]
    \addtolength{\itemsep}{-1.0\itemsep}}
  {\end{enumerate}}


\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,spacing=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage[american]{babel}
\usepackage{fourier}



\addpoints
\boxedpoints
\pointsinmargin
\pointname{pts}
\begin{document}
\large
\begin{flushleft}
\textbf{
Advanced Calculus I \\
Homework Assignment fake \\
Due Never  \the\year}\\
\vspace{0.25in}
Larry Kuúruks
\end{flushleft}

\noindent \emph{This assignment has questions 1 through \numquestions \/ with a total of \numpoints\/ points.  The box to the left of each question gives the point value for the question.  }


\vspace{0.25in}
\noindent \textbf{Link to Overleaf:} \url{https://www.overleaf.com/9215671327dfffbvstwbvp}

\begin{questions}

\question [2] Let $m,n$ be odd integers. Show that $m^2 + n^2$ is even.

\begin{solution}
Since $m$ and $n$ are odd integers, there are integers $k$ and $\ell$
such that $m=2 k + 1$ and $n = 2 \ell + 1$. We have
\begin{align*}
    m^2 + n^2 &= (2 k +1)^2 + (2 \ell + 1)^2, &\mbox{(substitution)} \\
              &= 4 k^2 + 4 k + 4 \ell^2 + 4 \ell + 2,  &\mbox{(expand)} \\
              &=2 (2 k^2 + 2 k + 2 + \ell^2 + 2 \ell + 1). &\mbox{(factor)}
\end{align*}
We've shown that $m^2 + n^2$ twice the integer $2 k^2 + 2 k + 2 + \ell^2 + 2\ell + 1 $; thus
$m^2 + n^2$ is even.
\end{solution}



\question[2] Let $n$ be an odd integer. Then $n^2 - 1$ is divisible by 8.

\question[2] Give two  examples of  sentences that are  \emph{not}  statements.

\begin{solution}
\begin{enumerate}
    \item Border collies are the \emph{best} dogs.
    \item Mathematics is discovered, not invented.
\end{enumerate}
\end{solution}
\question[2] Give two  examples of  sentences that are  statements.
\begin{solution}
    \begin{enumerate}
    \item The    absolute value        function is       continuous at zero.
    \item  Every perfect integer is even.
\end{enumerate}
\end{solution}


\question [2] Let $P$ be a statement. Show that $P \equiv \lnot \lnot P$ is a tautology.

\begin{solution}
A truth table is
\[
\begin{array}{|c | c |  c | c|} \hline
P & \lnot P & \lnot \lnot P & P \equiv \lnot \lnot P  \\ \hline \hline
T  & F & T & T \\ \hline
F  & T & F & T \\ \hline
\end{array}.
\]
Since the final column is all true, we've shown that $P \equiv \lnot \lnot P$ is a tautology.
\end{solution}

\end{questions}

\end{document}