\documentclass[12pt,fleqn]{exam}
\usepackage{pifont}
\usepackage{dingbat}
\usepackage{amsmath,amssymb}
\usepackage{epsfig}
\usepackage[]{hyperref}
\usepackage[letterpaper, margin=0.75in]{geometry}
\addpoints
\boxedpoints
\pointsinmargin
\pointname{pts}

\usepackage[activate={true,nocompatibility},final,tracking=true,kerning=true,factor=1100,stretch=10,shrink=10]{microtype}
\usepackage[american]{babel}
%\usepackage[T1]{fontenc}
\usepackage{fourier}
\usepackage{isomath}
\usepackage{upgreek,amsmath}
\usepackage{amssymb}

\newcommand{\dotprod}{\, {\scriptzcriptztyle
    \stackrel{\bullet}{{}}}\,}

\newcommand{\reals}{\mathbf{R}}
\newcommand{\lub}{\mathrm{lub}} 
\newcommand{\glb}{\mathrm{glb}} 
\newcommand{\complex}{\mathbf{C}}
\newcommand{\dom}{\mbox{dom}}
\newcommand{\cover}{{\mathcal C}}
\newcommand{\integers}{\mathbf{Z}}
\newcommand{\vi}{\, \mathbf{i}}
\newcommand{\vj}{\, \mathbf{j}}
\newcommand{\vk}{\, \mathbf{k}}
\newcommand{\bi}{\, \mathbf{i}}
\newcommand{\bj}{\, \mathbf{j}}
\newcommand{\bk}{\, \mathbf{k}}
\DeclareMathOperator{\Arg}{\mathrm{Arg}}
\DeclareMathOperator{\Ln}{\mathrm{Ln}}
\newcommand{\imag}{\, \mathrm{i}}
\newcommand{\range}{\mathrm{range}}
\newcommand{\ball}{\mathrm{ball}}
\newcommand{\LP}{\mathrm{LP}}

\usepackage{graphicx}
\newcommand\AM{{\sc am}}
\newcommand\PM{{\sc pm}}
     
\newcommand{\quiz}{10}
\newcommand{\term}{Fall}
\newcommand{\due}{Saturday 12 November at 11:59 \PM}
\begin{document}
\large
\vspace{0.1in}
\noindent\makebox[3.0truein][l]{{\bf MATH 460}}
{\bf Name:}  \\
\noindent \makebox[3.0truein][l]{\bf Homework \quiz, \term \/ \the\year}
%{\bf Row:}\hrulefill\
\vspace{0.1in}

\begin{quote}
    \fbox{I have neither given nor received unauthorized assistance on this assignment.}
    \end{quote}
\noindent  Homework    \quiz\/  has questions 1 through  \numquestions \/ with 
a total of  \numpoints\/  points.  Please neatly handwrite your solutions, digitize them and
submit the digitized copy to Canvas. This work is due \emph{\due}.

\vspace{0.1in}

%\noindent{\textbf{Link to your Overleaf work: }}\url{XXX}

\begin{questions} 

\question[5] Prove the product rule for derivatives. Specifically show
that if $f$ and $g$ are differentiable at $a$, then $f g$ is
differentiable at $a$. To do this use the Carathéodory definition
of the derivative. You may freely use the fact that the sum and
product of continuous functions is continuous.

\begin{solution}
    
\end{solution}

\question[5] Show that the function $x \in \reals \mapsto x |x|$ is
differentiable at zero.

\question[5] Let $f,g \in \reals \to \reals$. Either prove or find a 
counterexample: \emph{If $fg$ is differentiable at zero, either $f$
is differentiable at zero or $g$
is differentiable at zero.}



\question[5] Suppose $f,g \in \reals \to \reals$ are differentiable
at zero and suppose $f(0) = 0, g(0) = 0,$ and $g^\prime(0) \neq 0$.
Use the Carathéodory definition of the derivative to prove the 
L'Hôpital little theorem:
\begin{equation*}
\lim_{x \to 0} \frac{f(x)}{g(x)} = \frac{f^\prime(0)}{g^\prime(0)}.
\end{equation*}

\question (Bonus) There is at least one factual claim in the text

\url{http://mathonline.wikidot.com/carath-eodorys-differentiation-criterion}

that is rubbish and at least one grammatical error (I'd say far more than
one). What are these errors?
\end{questions}

\end{document}